PODD Ontology Driven Database

### 2012-03-08 epncanberra2012/Podd-20120313.tex
more changes to presentation

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{beamerthemenirma}

@@

\begin{itemize}
 \item Aim to test hypotheses in known, partially controlled situations
\pause
 \item Contain many variables
\pause
 \item Experiment variables are noted in workbooks
\end{itemize}

@@

\begin{itemize}
 \item Some common headings
\pause
 \item Structure can vary
\end{itemize}

@@

\begin{frame}
\frametitle{Tables}

\begin{itemize}
 \item Two dimensional structure
\pause
 \item Suit simple relationships
\pause
 \item Single table not ideal for entire experiment
\end{itemize}

\begin{frame}
\frametitle{Trees}

\begin{itemize}
 \item Everything has a common root
\pause
 \item Branches are independent of each other
\end{itemize}

@@

\begin{itemize}
 \item Vital metadata about each experiment
\pause
 \item Variable number of headings and subheadings
\pause
 \item Acceptable use of headings and subheadings is configurable
\pause
 \item Each workbook is independent of other workbooks
\end{itemize}

@@

\begin{itemize}
 \item Ontologies can be arbitrarily structured
\pause
 \item PODD has basic constraints
\begin{enumerate}
 \item Each ontology must have exactly one Project
 \item Each node must be connected to the Project through a series of ``part\_of'' links
 \item Each node can reference other nodes using ``refers\_to'' links
\end{enumerate}
\pause
\item Ontology defines acceptable structure without imposing a single schema on every workbook

\end{itemize}

@@

\begin{center}
 \includegraphics[scale=0.40,keepaspectratio=true]{./podd_ont.pdf}
 % podd_ont.pdf: 720x540 pixel, 72dpi, 25.40x19.05 cm, bb=0 0 720 540
\end{center}

>>>>

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{beamerthemeBerkeley}

@@

\begin{itemize}
 \item Aim to test hypotheses in known, partially controlled, situations
\pause
 \item Contain many variables
\pause
 \item Experiment variables and results are noted and used in analysis.
\pause
 \item Analysed results are used to make conclusions, which are published.
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Some common headings
\pause
 \item Structure can vary
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Relational databases}

\begin{itemize}
 \item Two dimensional structure
\pause
 \item Suit simple relationships
\pause
 \item Single table not ideal for entire experiment
\pause
 \item Not ideal for multiple different experiments
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Structured ontologies}

\begin{itemize}
 \item A common root
\pause
 \item Branches and leaves are independent of each other
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Vital metadata about each experiment in a single ontology
\pause
 \item Variable number of headings and subheadings
\pause
 \item Acceptable use of headings and subheadings is configurable
\pause
 \item Each experiment is independent of other experiments
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Ontologies allow different structures for different experiments without changing the underlying database schema
\pause
 \item PODD has basic constraints
\begin{enumerate}
 \item Each ontology must have exactly one Project
 \item Each node must be connected to the Project through a unique series of ``part\_of'' links
 \item Each node can reference other nodes using ``refers\_to'' links
\end{enumerate}
\pause
\item A single ontology can be used with different unique experiments if it is designed well
\end{itemize}
\end{frame}

@@

\begin{center}
 \includegraphics[scale=0.36,keepaspectratio=true]{./podd_ont.pdf}
 % podd_ont.pdf: 720x540 pixel, 72dpi, 25.40x19.05 cm, bb=0 0 720 540
\end{center}
\end{frame}

\begin{frame}
\frametitle{Publication}

\begin{itemize}
 \item Projects can be published on completion, both in HTML and RDF
\pause
 \item Published projects designed to be immutable
\pause
 \item Each data item has a URI
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Questions}

Code can be found online at:

\url{https://github.com/podd}
